As we use GD to solve SDA problem, we will introduce the related work on both areas.

In SDA, many works have been proposed to utilize the unlabeled data. Yao {et al.} \cite{yao2015semi} proposed a framework, named Semi-supervised Domain Adaptation with Subspace Learning (SDASL) to correct data distribution mismatch and leverages unlabeled data. Donahue {et al.}\cite{Donahue_2013_CVPR} proposed a framework for adapting classifiers by "borrowing" the source data to the target domain using a combination of available labeled and unlabeled examples. Daume {et al.} \cite{daume2010frustratingly} proposed a method by augmenting the feature space to compensate the domain shift. Duan {et al.} \cite{duan2012visual} proposed a method using the unlabeled data to measure the mismatch between the domains based on the maximum mean discrepancy.

There are also many works related to GD for computer vision tasks. Sharmanska et al. \cite{Sharmanska_2013_ICCV} proposed a Rank Transfer method that uses attributes, annotator
rationales, object bounding boxes, and textual descriptions as the privileged information for object recognition. Motiian et al. \cite{Motiian_2016_CVPR} proposed {the information bottleneck method with privileged information (IBPI)} that leverage the auxiliary information such as like supplemental visual features, bounding box annotations and 3D skeleton tracking data to improve visual recognition performance. Tzeng et al. \cite{Tzeng_2015_ICCV} proposed a CNN architecture for domain adaptation to leverage the knowledge from limited or no labeled data using the soft label. Urban et al. \cite{urban2016deep} use a small shallow net to mimick the output of a large deep net while using layer-wised distillation with $\ell_2$ loss of the outputs of student and teacher net. Similarly, Luo et al. \cite{luo2016face} use $\ell_2$ loss to train a compressed student model from the teacher model for face recognition. Gupta et al. \cite{Gupta_2016_CVPR} use supervision transfer to distill the knowledge from a trained CNN with unlabeled data or just a few labeled data.